Impact ionization processes in driven Mott insulating layer: influence of fermion baths and phonons

### 2022-07-21 figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_11_eph.tex
First draft 21.07.2022

\addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
\addlegendentry{$v=0.4$};
\addlegendimage{solid,color=hred,scale={1.0},line width=1pt} 
\addlegendentry{$v=0.8$};

@@

\addplot[solid,raw gnuplot,color=hblue,line width=1pt] gnuplot {
plot './Green_hyb0.4E3_O11.5.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.4E3_O11.5,solid,raw gnuplot,color=hblue,line width=1pt,opacity=0.0]gnuplot {
plot "./neq_distr_f_filling_hyb0.4E3_O11.5.dat" u 1:3 w l;
};

\addplot[solid,raw gnuplot,color=hred,line width=1pt] gnuplot {
plot './Green_hyb0.8E3_O11.5.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.8E3_O11.5,solid,raw gnuplot,color=hred,line width=1pt,opacity=0.0]gnuplot {
plot "./neq_distr_f_filling_hyb0.8E3_O11.5.dat" u 1:3 w l;
};

 \path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
 \addplot [fill=hblue,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4E3_O11.5 and xaxis,soft clip={domain=-15:15}]; 
 \addplot [fill=hred,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8E3_O11.5 and xaxis,soft clip={domain=-15:15}];

 \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(a)};
 \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$E_0=3$};

@@

\addlegendimage{solid,color=hcoral,scale={1.0},line width=1pt}
\addlegendentry{$v=0.4$};
\addlegendimage{solid,color=hlime,scale={1.0},line width=1pt} 
\addlegendentry{$v=0.8$};

@@

\addplot[solid,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
plot './Green_hyb0.4E4_O11.5.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.4E4_O11.5,solid,raw gnuplot,color=hcoral,line width=1pt,opacity=0.0]gnuplot {
plot "./neq_distr_f_filling_hyb0.4E4_O11.5.dat" u 1:3 w l;
};

\addplot[solid,raw gnuplot,color=hlime,line width=1pt] gnuplot {
plot './Green_hyb0.8E4_O11.5.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.8E4_O11.5,solid,raw gnuplot,color=hlime,line width=1pt,opacity=0.0]gnuplot {
plot "./neq_distr_f_filling_hyb0.8E4_O11.5.dat" u 1:3 w l;
};

 \path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
 \addplot [fill=hcoral,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4E4_O11.5 and xaxis,soft clip={domain=-15:15}]; 
 \addplot [fill=hlime,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8E4_O11.5 and xaxis,soft clip={domain=-15:15}];

 \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(b)};
 \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$E_0=4$};

>>>>

\addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
\addlegendentry{$el$};
\addlegendimage{solid,color=hred,scale={1.0},line width=1pt} 
\addlegendentry{$el+ph$};

@@

\addplot[solid,raw gnuplot,color=hblue,line width=1pt] gnuplot {
plot './Green_hyb0.4O11.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[dashed,raw gnuplot,color=hblue,line width=1pt] gnuplot {
plot './neq_distr_f_filling_hyb0.4O11.dat' u 1:3 w l;
};

\addplot[solid,raw gnuplot,color=hred,line width=1pt] gnuplot {
plot './Green_hyb0.4O11ph.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[dashed,raw gnuplot,color=hred,line width=1pt] gnuplot {
plot './neq_distr_f_filling_hyb0.4O11ph.dat' u 1:3 w l;
};

 \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(a)};
 \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$v=0.4$};

@@

\addlegendimage{solid,color=hcoral,scale={1.0},line width=1pt}
\addlegendentry{$el$};
\addlegendimage{solid,color=hlime,scale={1.0},line width=1pt} 
\addlegendentry{$el+ph$};

@@

\addplot[solid,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
plot './Green_hyb0.8O11.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[dashed,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
plot './neq_distr_f_filling_hyb0.8O11.dat' u 1:3 w l;
};

\addplot[solid,raw gnuplot,color=hlime,line width=1pt] gnuplot {
plot './Green_hyb0.8O11ph.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[dashed,raw gnuplot,color=hlime,line width=1pt] gnuplot {
plot './neq_distr_f_filling_hyb0.8O11ph.dat' u 1:3 w l;
};

 \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(b)};
 \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$v=0.8$};

### 2022-07-21 figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_5_11_e.tex
First draft 21.07.2022

\nextgroupplot[
xmin=-15.,      
xmax=15., 
ymin=0.00, 
ymax=0.09,   
minor tick num=1, 
% grid=both,
xlabel={$\omega/t^{*}$},
ylabel={$A(\omega)/t^{*-1}$},
legend style={at={(axis cs:-9.3,0.017)},anchor=north,mark options={scale=0.85},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
legend cell align=left,
clip mode=individual,
clip marker paths=true, 
xtick={-15,-10,-5,0,5,10,15},
ytick={0.00,0.03,0.06,0.09},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
x tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd},
y tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill, 
    precision=0, 
    /tikz/.cd}
]

\addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
\addlegendentry{$el$};
\addlegendimage{solid,color=hred,scale={1.0},line width=1pt} 
\addlegendentry{$el+ph$};

@@

\addplot[dashed,raw gnuplot,color=hblue,line width=1pt] gnuplot {
plot './neq_distr_f_filling_hyb0.4O11.dat' u 1:3 w l;
};

\addplot[solid,raw gnuplot,color=hred,line width=1pt] gnuplot {
plot './Green_hyb0.4O11ph.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[dashed,raw gnuplot,color=hred,line width=1pt] gnuplot {
plot './neq_distr_f_filling_hyb0.4O11ph.dat' u 1:3 w l;
};

 \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(a)};
 \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$v=0.4$};

\nextgroupplot[
xmin=-15.,     
xmax=15., 
ymin=0.00, 
ymax=0.09,   
minor tick num=1, 
% grid=both,
xlabel={$\omega/t^{*}$},
% ylabel={$A(\omega)/t^{*-1}$},
legend style={at={(axis cs:-9.3,0.017)},anchor=north,mark options={scale=0.85},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
legend cell align=left,
clip mode=individual,
clip marker paths=true, 
xtick={-15,-10,-5,0,5,10,15},
ytick={0.00,0.03,0.06,0.09},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
x tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd},
y tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd}
]

\addlegendimage{solid,color=hcoral,scale={1.0},line width=1pt}
\addlegendentry{$el$};
\addlegendimage{solid,color=hlime,scale={1.0},line width=1pt} 
\addlegendentry{$el+ph$};

\addplot[solid,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
plot './Green_hyb0.8O11.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[dashed,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
plot './neq_distr_f_filling_hyb0.8O11.dat' u 1:3 w l;
};

\addplot[solid,raw gnuplot,color=hlime,line width=1pt] gnuplot {
plot './Green_hyb0.8O11ph.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[dashed,raw gnuplot,color=hlime,line width=1pt] gnuplot {
plot './neq_distr_f_filling_hyb0.8O11ph.dat' u 1:3 w l;
};

 \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(b)};
 \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$v=0.8$};

>>>>

\nextgroupplot[
xmin=-15.,      
xmax=15., 
ymin=0.00, 
ymax=0.09,   
minor tick num=1, 
grid=both,
xlabel={$\omega/t^{*}$},
ylabel={$A(\omega)/t^{*-1}$},
legend style={at={(axis cs:0,0.1)},anchor=north,mark options={scale=1.0},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
legend cell align=left,
clip mode=individual,
clip marker paths=true, 
xtick={-15,-10,-5,0,5,10,15},
ytick={0.00,0.03,0.06,0.09},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
x tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd},
y tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0, 
    /tikz/.cd}
]

\addlegendimage{solid,color=hcoral,scale={1.0},line width=1pt}
\addlegendentry{$v=0.4$};
\addlegendimage{solid,color=hlime,scale={1.0},line width=1pt} 
\addlegendentry{$v=0.8$};

% \addplot +[dashed,very thin,color=hblue,mark=none] coordinates {(-2.55, 0.0) (-2.55, 0.035)};
% \addplot +[dashed,very thin,color=hblue,mark=none] coordinates {(0.525, 0.0) (0.525, 0.035)};
% \draw [stealth-stealth,thick,color=hblue](-2.55, 0.015) -- (0.525, 0.015);

% \addplot +[dashed,very thin,color=hred,mark=none] coordinates {(2.55, 0.0) (2.55, 0.035)};
% \addplot +[dashed,very thin,color=hred,mark=none] coordinates {(-0.525, 0.0) (-0.525, 0.035)};
% \draw [stealth-stealth,thick,color=hred](2.55, 0.02) -- (-0.525, 0.02);

% \draw [-stealth,thick,color=hgray](0.35, 0.0055) -- (0.45, 0.004);
% \draw [-stealth,thick,color=hgray](-0.35, 0.0055) -- (-0.45, 0.004);

% \draw [-stealth,thick,color=hgray](2.0, 0.0045) -- (2.2, 0.003);
% \draw [-stealth,thick,color=hgray](-2.0, 0.0045) -- (-2.2, 0.003);

\addplot[solid,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
plot './Green_hyb0.4O5.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.4O5,solid,raw gnuplot,color=hcoral,line width=1pt,opacity=0.0] gnuplot {
plot "neq_distr_f_filling_hyb0.4O5.dat" u 1:3 w l;
};

\addplot[solid,raw gnuplot,color=hlime,line width=1pt] gnuplot {
plot './Green_hyb0.8O5.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.8O5,solid,raw gnuplot,color=hlime,line width=1pt,opacity=0.0] gnuplot {
plot "neq_distr_f_filling_hyb0.8O5.dat" u 1:3 w l;
};

\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
\addplot [fill=hcoral,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O5 and xaxis,soft clip={domain=-15:15}];
\addplot [fill=hlime,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O5 and xaxis,soft clip={domain=-15:15}];

% \node[fill=none,color=hblue,scale={1.0}] at (axis cs:-1.20,0.017){$F$}; 
% \node[fill=none,color=hred,scale={1.0}] at (axis cs:1.20,0.022){$F$};
 \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(a)};
 \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$\Omega=5$};

\nextgroupplot[
xmin=-15.,     
xmax=15., 
ymin=0.00, 
ymax=0.09,   
minor tick num=1, 
grid=both,
xlabel={$\omega/t^{*}$},
% ylabel={$A(\omega)/t^{*-1}$},
legend style={at={(axis cs:0,0.1)},anchor=north,mark options={scale=1.0},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
legend cell align=left,
clip mode=individual,
clip marker paths=true, 
xtick={-15,-10,-5,0,5,10,15},
ytick={0.00,0.03,0.06,0.09},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
x tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd},
y tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd}
]

\addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
\addlegendentry{$v=0.4$};
\addlegendimage{solid,color=hred,scale={1.0},line width=1pt} 
\addlegendentry{$v=0.8$};

% \addplot +[dashed,very thin,color=hblue,mark=none] coordinates {(-2.55, 0.0) (-2.55, 0.035)};
% \addplot +[dashed,very thin,color=hblue,mark=none] coordinates {(0.525, 0.0) (0.525, 0.035)};
% \draw [stealth-stealth,thick,color=hblue](-2.55, 0.015) -- (0.525, 0.015);

% \addplot +[dashed,very thin,color=hred,mark=none] coordinates {(2.55, 0.0) (2.55, 0.035)};
% \addplot +[dashed,very thin,color=hred,mark=none] coordinates {(-0.525, 0.0) (-0.525, 0.035)};
% \draw [stealth-stealth,thick,color=hred](2.55, 0.02) -- (-0.525, 0.02);

% \draw [-stealth,thick,color=hgray](0.35, 0.0055) -- (0.45, 0.004);
% \draw [-stealth,thick,color=hgray](-0.35, 0.0055) -- (-0.45, 0.004);

% \draw [-stealth,thick,color=hgray](2.0, 0.0045) -- (2.2, 0.003);
% \draw [-stealth,thick,color=hgray](-2.0, 0.0045) -- (-2.2, 0.003);

@@

\addplot[name path=neq_distr_f_filling_hyb0.4O11,solid,raw gnuplot,color=hblue,line width=1pt,opacity=0.0] gnuplot {
plot "neq_distr_f_filling_hyb0.4O11.dat" u 1:3 w l;
};

\addplot[solid,raw gnuplot,color=hred,line width=1pt] gnuplot {
plot './Green_hyb0.8O11.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.8O11,solid,raw gnuplot,color=hred,line width=1pt,opacity=0.0] gnuplot {
plot "neq_distr_f_filling_hyb0.8O11.dat" u 1:3 w l;
};

\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
\addplot [fill=hblue,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11 and xaxis,soft clip={domain=-15:15}];
\addplot [fill=hred,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O11 and xaxis,soft clip={domain=-15:15}];

% \node[fill=none,color=hblue,scale={1.0}] at (axis cs:-1.20,0.017){$F$};
% \node[fill=none,color=hred,scale={1.0}] at (axis cs:1.20,0.022){$F$};
 \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(b)};
 \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$\Omega=11$};
